Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
install.packages("ggplot2")

library(ggplot2)
pf <- read.csv('~/dev/udacity_coursework/data_analysis_with_r-ud651/data/pseudo_facebook.tsv', sep = '\t')

list.files()
qplot(x = age, y = friend_count, data=pf)
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
qplot(x = age, y = friend_count, data=pf)

ggplot(aes(x = age, y = friend_count), data=pf) +
  geom_point()

summary(pf$age)

# add xlim
ggplot(aes(x = age, y = friend_count), data=pf) +
  geom_point() +
  xlim (13, 90)


```

***

### Overplotting
Notes:

```{r Overplotting}
# set alpha so that you can tell how many points are in a region
ggplot(aes(x = age, y = friend_count), data=pf) +
  geom_point(alpha = 1/20) +
  xlim (13, 90)

# use geom_jitter instead of geom_point
ggplot(aes(x = age, y = friend_count), data=pf) +
  geom_jitter(alpha = 1/20) +
  xlim (13, 90)
```

#### What do you notice in the plot?
Response: the same trend is evident but isn't as drastic as we thought. There is still overplotting happening in the lower regions of the plot

***

### Coord_trans()
Notes:

```{r Coord_trans()}

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}
ggplot(aes(x = age, y = friend_count), data=pf) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim (13, 90) +
  coord_trans(y = 'sqrt')
```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data=pf) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim (13, 90) +
  coord_trans(y = 'sqrt')
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
install.packages('dplyr')
library(dplyr)

age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups,
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n())
pf.fc_by_age <- arrange(pf.fc_by_age)
head(pf.fc_by_age)

# very cool alt code
pf.fc_by_age <- pf %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age)

head(pf.fc_by_age, 20)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age, y = friend_count_mean), data=pf.fc_by_age) +
  geom_line() +
  xlim (13, 90)
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friendships_initiated), data=pf) +
  geom_point(alpha = 1/20,
             position = position_jitter(h = 0),
             color = 'orange') +
  xlim (13, 90) +
  coord_trans(y = 'sqrt') +
  geom_line(stat = 'summary', fun.y = mean) +
#TODO probs doesn't work
  # geom_line(stat = 'summary', fun.y = quantile, probs = .1)
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(pf$age, pf$friend_count, method = 'pearson')
with(pf, cor.test(age, friend_count, method = 'pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:likes received vs www likes received

```{r}
ggplot(data = pf, aes(x = www_likes_received, y = likes_received)) +
  geom_point() +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0, quantile(pf$likes_received, 0.95)) +
  geom_smooth(method = 'lm', color = 'red')
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
with(pf, cor.test(www_likes_received, likes_received, method = 'pearson'))
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.
0
b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
today <- c(2015, 01, 12)
pf$age_with_months <- pf$age + (12-pf$dob_month)/12
```

***

### Age with Months Means

```{r Age with Months Means}
library(dplyr)
pf.fc_by_age_months <- pf %>%
  group_by(age_with_months) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age_with_months)
```

Programming Assignment
```{r Programming Assignment}
p1 <- ggplot(data = subset(pf.fc_by_age, age < 71),
             aes(x = age, y = friend_count_mean)) +
  geom_line()

p2 <- ggplot(data = subset(pf.fc_by_age_months, age_with_months < 71),
             aes(x = age_with_months, y = friend_count_mean)) +
  geom_line()

p3 <- ggplot(data = subset(pf, age < 71),
             aes(x = round(age/5)*5, y = friend_count)) +
  geom_line(stat = 'summary', fun.y = mean)

library(gridExtra)
grid.arrange(p2, p1, p3, ncol = 1)
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

