---
title: "Gapminder Data"
author: '@IanEdington'
date: "December 21, 2015"
output: html_document
---

The Gapminder website contains over 500 data sets with information about
the world's population. Your task is to download a data set of your choice
and create 2-5 plots that make use of the techniques from Lesson 3.

You might use a simple histogram, a boxplot split over a categorical variable,
or a frequency polygon. The choice is yours!

You can find a link to the Gapminder website in the Instructor Notes.

Once you've completed your investigation, create a post in the discussions that includes:
      1. any questions you answered, your observations, and summary statistics
      2. snippets of code that created the plots
      3. links to the images of your plots

You can save images by using the ggsave() command.
ggsave() will save the last plot created.
For example...
                 qplot(x = price, data = diamonds)
                 ggsave('priceHistogram.png')

ggsave currently recognises the extensions eps/ps, tex (pictex),
pdf, jpeg, tiff, png, bmp, svg and wmf (windows only).

Copy and paste all of the code that you used for
your investigation, and submit it when you are ready.
====================================================================================

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)

```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
