---
title: "lesson3_problemset"
output: html_document
---

1. Diamonds
  How many observations are in the data set? : 53940
  How many variables are in the data set? : 10
  How many ordered factors are in the dataset? : 3 (cut, colour, clarity)
  What letter represents the best colour for a diamond? : D

```{r}
library(ggplot2)
data(diamonds)
nrow(diamonds) # Number of observations
summary(diamonds) # Variables in dataset
?diamonds # Ordered Factors, Best Colour
```

2. Create a histogram of the price of all the diamonds in the diamond data set.

```{r}
qplot(price, data = diamonds)
```

3. Price Histogram Summary

```{r}
summary(diamonds$price)
mean(diamonds$price)
```

4. Diamond Counts
  How many diamonds cost less than $500?
  How many diamonds cost less than $250?
  How many diamonds cost $15,000 or more?

```{r}
?subset
nrow(subset(diamonds, price < 500)) # less than 500
nrow(subset(diamonds, price < 250)) # less than 250
nrow(subset(diamonds, price >= 15000)) # more than or equal to 15,000
```

5. Cheaper Diamonds
Explore the largest peak in the price histogram you created earlier. Try limiting the x-axis, altering the bin width, and setting different breaks on the x-axis.

```{r}
hist <- qplot(diamonds$price) +
  coord_cartesian(xlim = c(0, 5000)) # This doesn't change graph only view

hist + scale_x_continuous(limits = c(500, 1500)) # Actually subsets the data
hist + xlim(500, 1500) # Short hand for the same thing

qplot(diamonds$price, binwidth = 50) +
  scale_x_continuous(limits = c(500, 1500), breaks=seq(500,1500,100))
```

6. Break out histograms by cut (Price by Cut Histograms)

```{r}
qplot(price, data = diamonds) + facet_wrap(~cut)
  # had to change qplot to include data, else it doesn't have info on cut
```

7. Price by Cut

Which cut has the 1. Highest priced diamond
                  2. Lowest priced diamond
                  3. Lowest median price

```{r}
by(diamonds$price, diamonds$cut, max)
by(diamonds$price, diamonds$cut, min)
by(diamonds$price, diamonds$cut, median)
```

8. When you facet_wrap over cut the y scale is fixed. How do you make the y scale different for different facets?

```{r}
qplot(x = price, data = diamonds) + facet_wrap(~cut, scales = "free_y")
```

9. Price per Carat by Cut

Create a histogram of price per carat and facet it by cut. You can make adjustments to the code from the previous exercise to get started.

Adjust the bin width and transform the scale of the x-axis using log10.

```{r}
diamonds$pricePerCarat <- diamonds$price / diamonds$carat

qplot(x = pricePerCarat, data = diamonds) +
  facet_wrap(~cut, scales = "free_y") +
  scale_x_log10()
```


