---
title: "lesson3_problemset"
output: html_document
---

1. Diamonds
  How many observations are in the data set? : 53940
  How many variables are in the data set? : 10
  How many ordered factors are in the dataset? : 3 (cut, colour, clarity)
  What letter represents the best colour for a diamond? : D

```{r}
library(ggplot2)
data(diamonds)
nrow(diamonds) # Number of observations
summary(diamonds) # Variables in dataset
?diamonds # Ordered Factors, Best Colour
```

2. Create a histogram of the price of all the diamonds in the diamond data set.

```{r}
qplot(price, data = diamonds)
```

3. Price Histogram Summary

```{r}
summary(diamonds$price)
mean(diamonds$price)
```

4. Diamond Counts
  How many diamonds cost less than $500?
  How many diamonds cost less than $250?
  How many diamonds cost $15,000 or more?

```{r}
?subset
nrow(subset(diamonds, price < 500)) # less than 500
nrow(subset(diamonds, price < 250)) # less than 250
nrow(subset(diamonds, price >= 15000)) # more than or equal to 15,000
```

